Calculating Biological Module Enrichment or Depletion and Visualizing Data on Large-scale Molecular Maps with ACSNMineR and RNaviCell packages

### 2016-03-14 jss/ACSNMineR.tex
Edited abstract
[skip ci]

%% an abstract and keywords
\abstract{
Biological pathways or modules represent sets of interactions or functional 
relationships occurring at the molecular level in living cells. A large body 
of knowledge on pathways is organized in public databases such as the KEGG,
Reactome, or in more specialized repositories, the Atlas of Cancer Signaling 
Network (ACSN) being an example. All these open and popular biological databases
facilitate analyses, improving our understanding of cellular systems. Here we describe
\CRANpkg{ACSNMineR} for calculation of enrichment or depletion
of gene-lists of interest in biological pathways. It has integrated ACSN molecular
pathways, but can use any molecular pathway encoded as a GMT file, for instance sets 
of genes available in the Molecular Signatures Database (MSigDB). We also present 
\CRANpkg{RNaviCell},that can be used in conjunction with \pkg{ACSNMineR} to
visualize different data types on web-based, interactive ACSN maps. We
illustrate the functionalities of the two packages with biological
data taken from large-scale cancer datasets.

>>>>

%% an abstract and keywords
\abstract{
Biological pathways or modules represent sets of interactions or functional relationships occurring at the molecular level in living cells. A large body of knowledge on pathways is organized in public databases such as the KEGG, Reactome, or in more specialized repositories, the Atlas of Cancer Signaling Network (ACSN) being an example. All these open biological databases facilitate analyses, improving our understanding of cellular systems. We hereby describe \CRANpkg{ACSNMineR} for calculation of enrichment or depletion of lists of genes of interest in biological pathways. \pkg{ACSNMineR} integrates ACSN molecular pathways, but can use any molecular pathway encoded as a GMT file, for instance sets of genes available in the Molecular Signatures Database (MSigDB). We also present \CRANpkg{RNaviCell}, that can be used in conjunction with \pkg{ACSNMineR} to visualize different data types on web-based, interactive ACSN maps. We illustrate the functionalities of the two packages with biological data taken from large-scale cancer datasets.
